Titeln på avhandlingens språk

### 2023-01-16 body/part1/overview/extending-wca.tex
writing

>>>>

\begin{figure}
    \centering
    \includegraphics[height=13em]{publications/2023EdgeDroid2/model_data/frame_probabilities}
    \caption{%
        Distribution of processing results for frames captured during the execution of steps in the LEGO task.
        Note that \emph{Success} results are not included since by definition \ensuremath{P(\text{Success}|t_i) = 1.0} for all normalized instants \ensuremath{t_i \geq 1.0}.
    }
    \label{fig:modelframes}
\end{figure}

Our design for a procedure for the generation of synthetic yet realistic traces of video inputs for \gls{WCA} is based on a stochastic approach.
Analysis of the distribution of processing results of frames during the execution of steps in the LEGO task highlighted a pattern that was independent from execution times, illustrated in
